Veasel meets FOX: an ensemble approach to entity linking based on vector similarity

### 2015-07-10 paper.tex
minor update

We evaluate our entity linking approach on two datasets, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}} \cite{spotlight},  
in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:

>>>>

We evaluate our entity linking approach on two datasets, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},  
in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:
